The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
better edge descriptions

## Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on predicted social (visual and auditory perception), spatial
(habitat type), and temporal (seasonal) scales. Caribou are gregarious ungulates
with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
is presumed to be a costly behaviour and as a result, caribou tend to occupy and
re-use craters once they are established and there is considerably less access
to forage than when the landscape is snow-free. Importantly, craters exist on
the landscape at multiple scales: the crater scale (a single crater), the
feeding area scale (multiple craters in close proximity), and the winter range
scale (all craters within an individual’s range) [@Mayor_2009]. The distribution
of forage for caribou is therefore seasonally heterogeneous because the
distribution of craters on the landscape varies meaning that access to
vegetation in winter is highly variable for caribou. Caribou therefore have
greater access to forage in snow-free seasons. We  partitioned data into two
discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
February 2018) based on caribou socioecology [@Peignier_2019].

@@

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, nodes represented individuals, intralayer edges represented
associations between individuals in a given habitat type and season, and
interlayer edges represented connections between the same individuals across
seasons and within habitat classes (Figure 2).
<!-- eg this is connecting contexts used to calculate layer similarity -->

>>>>

## Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on predicted social (visual and auditory perception), spatial
(habitat type), and temporal (seasonal) scales. Caribou are gregarious ungulates
with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
is presumed to be a costly behaviour and as a result, caribou tend to occupy and
re-use craters once they are established and there is considerably less access
to forage than when the landscape is snow-free. Importantly, craters exist on
the landscape at multiple scales: the crater scale (a single crater), the
feeding area scale (multiple craters in close proximity), and the winter range
scale (all craters within an individual’s range) [@Mayor_2009]. The distribution
of forage for caribou is therefore seasonally heterogeneous because the
distribution of craters on the landscape varies meaning that access to
vegetation in winter is highly variable for caribou in winter compared to summer. Caribou therefore have
greater access to forage in snow-free seasons. We  partitioned data into two
discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
February 2018) based on caribou socioecology [@Peignier_2019].

@@

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes, associations between
individuals in a given habitat type and season were represented as intralayer
edges, and connections between the same individuals across seasons and within
habitat classes were represented as interlayer edges (Figure 2) .
<!-- eg this is connecting contexts used to calculate layer similarity -->
